\documentclass{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}

\title{Development Plan\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}


\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
23--09--2024 & Inreet & Introduction\\
23--09--2024 & Inreet & Confidential Information\\
23--09--2024 & Inreet & IP to Protect\\
23--09--2024 & Gurleen & Copyright License\\
23--09--2024 & Gurleen & Team meeting Plan\\
23--09--2024 & Gurleen & Team Communication Plan\\
23--09--2024 & Inreet & Team member Roles\\
23--09--2024 & Inreet, Pranav & Workflow Plan\\
23--09--2024 & Inreet & Project Decomposition and Scheduling\\
23--09--2024 & Pranav & Proof of Concept Demonstration Plan\\
23--09--2024 & Pranav & Expected Technology\\
23--09--2024 & Gurleen & Coding Standards\\
23--09--2024 & All & Reflection\\
23--09--2024 & Inreet & Team Charter\\
23--09--2024 & Pranav & Review + Fix Compilation Errors\\
... & ... & ...\\
\bottomrule
\end{tabularx}
\end{table}

\newpage{}

This document will provide details about various essential aspects of our development plan. It covers information about critical areas such as confidential information, IPs, and copyright considerations ensuring compliance with ethical standards and regulatory requirements. In addition to this, we will outline team meetings communication plans, and team member roles. We will include a workflow plan that describes how we plan to use Git and GitHub projects for workflow plans and project decompositions and scheduling. Moreover, we have incuded a proof-of-concept demonstration plan along with the technology stack and coding standards we wish for the development of our project. Finally, we will reflect on our learning from this exercise and include a team charter that defines our goals, expectations, and decision-making strategy. 

\wss{Additional information on the development plan can be found in the
\href{https://gitlab.cas.mcmaster.ca/courses/capstone/-/blob/main/Lectures/L02b_POCAndDevPlan/POCAndDevPlan.pdf?ref_type=heads}
{lecture slides}.}

\section{Confidential Information?}

Our project would not use any confidential data and information from the industry. We plan to use publicly available data in the development of this application, ensuring there is no breach of confidentiality.

\section{IP to Protect}

There is no IP to protect this project at the current stage. All work during the development phase will be original and no existing patents or proprietary technologies are involved. 

\section{Copyright License}

\wss{What copyright license is your team adopting.  Point to the license in your
repo.}

\section{Team Meeting Plan}

\wss{How often will you meet? where?}

\wss{If the meeting is a physical location (not virtual), out of an abundance of
caution for safety reasons you shouldn't put the location online}

\wss{How often will you meet with your industry advisor?  when?  where?}

\wss{Will meetings be virtual?  At least some meetings should likely be
in-person.}

\wss{How will the meetings be structured?  There should be a chair for all meetings.  There should be an agenda for all meetings.}

\section{Team Communication Plan}

\wss{Issues on GitHub should be part of your communication plan.}

\section{Team Member Roles}
 
The team would have the following distribution of administrative roles.

\begin{itemize}
\item Project Leader: Pranav Kalsi
\begin{itemize}
\item Prepare agenda for team meetings, ensuring all relevant topics are covered and goals are clear
\item Assign issues on the Kanban board, tracking the progress of each task and redistributing work if needed
\item Act as a liaison between the group and instructional team
\end{itemize}

\item Notetaker: Gurleen Kaur
\begin{itemize}
\item Record meeting minutes and attendance during team meetings
\item Assist in updating the Kanban board based on meeting outcomes
\end{itemize}

\item Communication Laison: Moamen Ahmed
\begin{itemize}
\item Organize team meetings and send reminders to all team members
\item Schedule meetings with external stakeholders
\end{itemize}

\item Administrator: Inreet Kaur
\begin{itemize}
\item Submit Deliverables on the avenue and ensure they meet the requirements
\item Maintain project documentation and files
\end{itemize}
\end{itemize} 

The team will remain flexible for the following roles, with responsibilities subject to change based on the needs of each deliverable and the final project:

Meeting Chair: This role will rotate between team members. The chair will organize and lead meetings, ensuring that the agenda is followed, and discussions stay focused.

Reviewer: The team plans to distribute each milestone evenly among the team members. Each team member’s work will be reviewed by at least two other team members. The reviewer will update issues on GitHub with appropriate comments.

Subject researcher: During a deliverable team members may be assigned to gather information about the industry, their processes, and information about the technology used in development. This role will shift based on individual expertise.

By adopting a flexible approach to the following roles, we want to ensure that everyone has the opportunity to lead and adapt their role according to the project’s needs. Regular check-ins during the team meetings will allow the team to reassess the roles and redistribute tasks as needed. 


\section{Workflow Plan}

We will utilize Git as our version control throughout this project. Here is a detailed breakdown of how we collaborate using different features on GitHub. 

\begin{itemize}
\item Branches: We will create different branches related to each task or issue. 
\begin{itemize}
\item Main branch: The main branch will have a stable production-ready code. 
\item Feature branches: All features will be assigned their own branch. Once tested it will be merged into the main branch.
\item Documentation branches: Each team member will create their branch when working on a particular documentation task. 
\end{itemize}

\item Pull requests: Once a feature is ready for production or some documentation is ready, team members will create a pull request to merge them into the main branch. Each commit should include a brief description of the changes and related issue numbers of the Kanban board.

\item Issue tracking: The team will utilize the Kanban board under projects for issue tracking. The team will use the provided templates for the appropriate issues and create its own where needed. 
\end{itemize}

The team will be using the following projects:

\begin{itemize}
\item Metrics: This project will be used to record metrics such as attended lectures and team meetings. It has two types of Issues lecture meetings and team meetings and uses the appropriate templates provided. Each team member adds their own attendance and updates team meeting notes as per their assigned roles.
\item Documentation: This project is used to create issues for each assigned task related to project documentation. Each issue will be reviewed by at least two other team members. Each issue uses a customized documentation template and is classified based on different milestones of project documentation. 
\item Development workflow: This project will be used to record issues for different features, feature enhancement, bug fixes, and other needs of the project. The issues will be divided into the above-listed categories and will use customized templates for each. 
\end{itemize}

CI/CD will be critical for project development. We will be using \textbf{Jenkins} which is an open-source CI/CD development tool that will act as an automated DevOps tool.

Jenkins will allow us to achieve Continuous Integration and Continuous Delivery through the following:
\begin{itemize}
  \item \textbf{Continuous Integration} -- On the continuous integration time Jenkins offers automated build and testing. This will save a lot of overhead on testing and test feedback as Jenkins will be responsible for it as not only will it build and test the code it will offer instant feedback to the developer.
  \item \textbf{Continuous Deployment} -- Jenkins offer automated deployment functionalities meaning that once the build passes all test it can be deployed into a production or pre-production environment. This will ensure the deployment is consistent, reliable, and efficient. This also will make sure that all features pass a minimum functionality standard ensuring that they are ready for production. Jenkins offers intragrations with git as well so deployments will be version controlled meain they may be reverted as needed.
\end{itemize}

By implemening a CI/CD tool (Jenkins) we can ensure that code isn't riddled with errors and automate a lot of task which will increase productivity. Having Jenkins also will reduce the risk of human error in the project and will automate many areas of DevOps. 

\section{Project Decomposition and Scheduling}

The team will utilize Kanban Board Projects for Issue tracking with four different stages of an issue: ‘To Do’, ‘In Progress’, ‘Review’, and ‘Done’. The team will create different issues for features, bugs, documentation, team meetings, lecture meetings and other things as needed using appropriate templates. The team will create templates for features, bugs and documentation. Issues under different projects will be classified into different milestones with appropriate deadlines. This will help us to track our progress for major milestones in the project. 
Futhermore, we will divide the Kanban board issues into sprints, therefore we can reduce the risk of the overall project. Sprints will ensure that the risk of the project is lowered as we will be working in an agile fashion.

Project Links:
\begin{itemize}
\item  
\href{https://github.com/users/Inreet-Kaur/projects/4}{Metrics}
\item  
\href{https://github.com/users/Inreet-Kaur/projects/2}{Documentation} 
\item 
\href{https://github.com/users/Inreet-Kaur/projects/6}{Development workflow}
\end{itemize}

Here is a general process that our team will follow to work on each issue. The team leader will create different issues under the ‘To do’ section and assign them to different team members as discussed during team meetings. Once the changes have been made the team members can now move the issue under the ‘Review’ tab and assign it to other members. The reviewers will provide appropriate comments and suggested changes and move the issue to the ‘In progress’ section if needed. Each issue will be reviewed by at least two other team members. Once the final changes are approved, the issue will now be moved to the ‘Done’ section. 

Each project will be scheduled according to the deadlines outlined in the course outline. The documentation project will have a separate milestone for each deliverable mentioned in the course outline along with the appropriate deadline. The metrics project will track all the team meetings, lecture attendance, and other metrics required throughout the course. We will create an issue for each lecture and each team meeting with the required details in the template. The development project will be classified into different milestones throughout this course. Some stages include initial feature planning, Phase 1 which includes developing core functionalities, including voice recording and chart filling, and Phase 2 which includes developing additional features like the analytical dashboard, triage integration etc. Each phase will have separate issues for feature development, bug fixes, enhancement, and final reviews. 

\section{Proof of Concept Demonstration Plan}

What is the main risk, or risks, for the success of your project?  What will you
demonstrate during your proof of concept demonstration to convince yourself that
you will be able to overcome this risk?\\

The main risk of the project is related to the reduction of documentation overhead. This means the biggest risk is really if this project can make a significant reduction to overhead time and trulty reduce patient wait times. Again, through ellicitation and our domain experts we will create an effective set of requirments to reduce the risk of the project and build something that is needed.\\

Through our development plan, the coding standards, and agile approach the development risk is made to be lower than an herculean approach. Therefore due to our development approach and using an agile workflow the projects risk will be reduced as features will be created overtime.\\

Looking at implementation details there are a few risks that come up, if these risks can be addressed or have a clearer roadmap that will make us more confident in the project. 

\begin{itemize}
  \item \textbf{Speech Input} -- A hospital or a clinic can be a loud place, in the event audio input is taken we need to ensure that it is clean and clear. This would be mean essentially blocking outside noise. 
  \item \textbf{Visual Inputs} -- If any old charts are needing to be inputted into the patient journey having the ability to scan and transfer the information into the required format will be another risk. The document needs to be rid of noisy data.
  \item \textbf{Pre-Trained Models} -- To manipulate and use both inputs above we need to create a model to be accurate and provide accuracy when filling in charts. 
  \item \textbf{Data privacy} -- This application will hold a lot of patient data so create a store that is secure and making sure standard data security practice is applied is a must.
  \item \textbf{User Acceptance} -- This will require further ellicitation outside supervisors. We need to gather data on what critical needs are on healthcare professionals such that critical features are present. 
\end{itemize}

\section{Expected Technology}

\wss{What programming language or languages do you expect to use?  What external
libraries?  What frameworks?  What technologies.  Are there major components of
the implementation that you expect you will implement, despite the existence of
libraries that provide the required functionality.  For projects with machine
learning, will you use pre-trained models, or be training your own model?  }

\wss{The implementation decisions can, and likely will, change over the course
of the project.  The initial documentation should be written in an abstract way;
it should be agnostic of the implementation choices, unless the implementation
choices are project constraints.  However, recording our initial thoughts on
implementation helps understand the challenge level and feasibility of a
project.  It may also help with early identification of areas where project
members will need to augment their training.}

Topics to discuss include the following:


In terms of expected technologies we need expect will again change will implementation details and architectures. Below is a starting point for a microservices based architecture.


\begin{itemize}
  \item Programming languages/Frameworks and Data managment:
    \begin{itemize}
      \item ReactJS -- This will be used for the frontend of the application.
      \item Python (Flask) -- This will be used to write backend services.
      \item Java (SpringBoot) -- This will also provide an alternative option for backend services, it could be specifically be useful for MongoDB intergration.
      \item MongoDB -- All data will be managed through a MongoDB database as it offers built in caching and performs well under load.
      \item Distributed Cache (Redis) -- Items that make be frequent calls can be cached through redis. This will overall increase the performance of the application.
    \end{itemize}
    

  \item Libraries
    Key frameworks have be
    \begin{itemize}
      \item LangChain -- This will be used for and LLM intergrations as it offers integrations will all of big LLMs.
      \item NLTK -- NLTK will be used for any natural language processing needs. 
      \item Redux -- Redux will be critical in managing frontend states.
      \item OAuth -- OAuth will be critical in microservices communication to validate the services. This will especially come in handy in a specific middleware layer is implemented.
    \end{itemize}

  \item Specific linter tool -- Linters are useful for catching errors early in the development process. This also ensure the code that is written adhere to the standard which will mitigate code smells and enforce a specific style. Linters we can use include PyLint (Python), PMD for error catching, and/or Checkstyle to ensure the required coding standard is upheld.
  \item Specific unit testing framework -- For frontend testing we can use selenium to interact with the front and leverage frameworks like JUnit for backend unit testing. 
    
  \item Investigation of code coverage measuring tools -- language specific code coverage tools will be used such as Coverage.py for python to assess coverage metrics and which cases are tested for.
  \item Continuous integration -- As stated above Jenkins will be used to automate a lot of CI tasks. Please refer to the CI/CD section above.

  \item Tools we will be using include Git, GitHub, and GitHub projects for development. This will mean using version control as be thwe workflow plan above, and planning features and sprints based on GitHub projects. 
\end{itemize}


\wss{git, GitHub and GitHub projects should be part of your technology.}

\section{Coding Standard}

\wss{What coding standard will you adopt?}

\newpage{}

\section*{Appendix --- Reflection}

\wss{Not required for CAS 741}

\input{../Reflection.tex}

\begin{enumerate}
    \item Why is it important to create a development plan prior to starting the
    project?
    \item In your opinion, what are the advantages and disadvantages of using
    CI/CD?
    \item What disagreements did your group have in this deliverable, if any,
    and how did you resolve them?
\end{enumerate}

\newpage{}

\section*{Appendix --- Team Charter}

\wss{borrows from
\href{https://engineering.up.edu/industry_partnerships/files/team-charter.pdf}
{University of Portland Team Charter}}

\subsection*{External Goals}

\wss{What are your team's external goals for this project? These are not the
goals related to the functionality or quality fo the project.  These are the
goals on what the team wishes to achieve with the project.  Potential goals are
to win a prize at the Capstone EXPO, or to have something to talk about in
interviews, or to get an A+, etc.}

\subsection*{Attendance}

\subsubsection*{Expectations}

\wss{What are your team's expectations regarding meeting attendance (being on
time, leaving early, missing meetings, etc.)?}

\subsubsection*{Acceptable Excuse}

\wss{What constitutes an acceptable excuse for missing a meeting or a deadline?
What types of excuses will not be considered acceptable?}

\subsubsection*{In Case of Emergency}

\wss{What process will team members follow if they have an emergency and cannot
attend a team meeting or complete their individual work promised for a team
deliverable?}

\subsection*{Accountability and Teamwork}

\subsubsection*{Quality} 

\wss{What are your team's expectations regarding the quality
of team members' preparation for team meetings and the quality of the
deliverables that members bring to the team?}

\subsubsection*{Attitude}

\wss{What are your team's expectations regarding team members' ideas,
interactions with the team, cooperation, attitudes, and anything else regarding
team member contributions?  Do you want to introduce a code of conduct?  Do you
want a conflict resolution plan?  Can adopt existing codes of conduct.}

\subsubsection*{Stay on Track}

\wss{What methods will be used to keep the team on track? How will your team
ensure that members contribute as expected to the team and that the team
performs as expected? How will your team reward members who do well and manage
members whose performance is below expectations?  What are the consequences for
someone not contributing their fair share?}

\wss{You may wish to use the project management metrics collected for the TA and
instructor for this.}

\wss{You can set target metrics for attendance, commits, etc.  What are the
consequences if someone doesn't hit their targets?  Do they need to bring the
coffee to the next team meeting?  Does the team need to make an appointment with
their TA, or the instructor?  Are there incentives for reaching targets early?}

\subsubsection*{Team Building}

\wss{How will you build team cohesion (fun time, group rituals, etc.)? }

\subsubsection*{Decision Making} 

\wss{How will you make decisions in your group? Consensus?  Vote? How will you
handle disagreements? }

\end{document}