% THIS DOCUMENT IS TAILORED TO REQUIREMENTS FOR SCIENTIFIC COMPUTING.  IT SHOULDN'T
% BE USED FOR NON-SCIENTIFIC COMPUTING PROJECTS
\documentclass[12pt]{article}

\usepackage{amsmath, mathtools}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{colortbl}
\usepackage{xr}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{xfrac}
\usepackage{tabularx}
\usepackage{float}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{pdflscape}
\usepackage{afterpage}

\usepackage[round]{natbib}

%\usepackage{refcheck}

\hypersetup{
    bookmarks=true,         % show bookmarks bar?
      colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

\input{../Comments}
\input{../Common}

% For easy change of table widths
\newcommand{\colZwidth}{1.0\textwidth}
\newcommand{\colAwidth}{0.13\textwidth}
\newcommand{\colBwidth}{0.82\textwidth}
\newcommand{\colCwidth}{0.1\textwidth}
\newcommand{\colDwidth}{0.05\textwidth}
\newcommand{\colEwidth}{0.8\textwidth}
\newcommand{\colFwidth}{0.17\textwidth}
\newcommand{\colGwidth}{0.5\textwidth}
\newcommand{\colHwidth}{0.28\textwidth}

% Used so that cross-references have a meaningful prefix
\newcounter{defnum} %Definition Number
\newcommand{\dthedefnum}{GD\thedefnum}
\newcommand{\dref}[1]{GD\ref{#1}}
\newcounter{datadefnum} %Datadefinition Number
\newcommand{\ddthedatadefnum}{DD\thedatadefnum}
\newcommand{\ddref}[1]{DD\ref{#1}}
\newcounter{theorynum} %Theory Number
\newcommand{\tthetheorynum}{TM\thetheorynum}
\newcommand{\tref}[1]{TM\ref{#1}}
\newcounter{tablenum} %Table Number
\newcommand{\tbthetablenum}{TB\thetablenum}
\newcommand{\tbref}[1]{TB\ref{#1}}
\newcounter{assumpnum} %Assumption Number
\newcommand{\atheassumpnum}{A\theassumpnum}
\newcommand{\aref}[1]{A\ref{#1}}
\newcounter{goalnum} %Goal Number
\newcommand{\gthegoalnum}{GS\thegoalnum}
\newcommand{\gsref}[1]{GS\ref{#1}}
\newcounter{instnum} %Instance Number
\newcommand{\itheinstnum}{IM\theinstnum}
\newcommand{\iref}[1]{IM\ref{#1}}
\newcounter{reqnum} %Requirement Number
\newcommand{\rthereqnum}{R\thereqnum}
\newcommand{\rref}[1]{R\ref{#1}}
\newcounter{nfrnum} %NFR Number
\newcommand{\rthenfrnum}{NFR\thenfrnum}
\newcommand{\nfrref}[1]{NFR\ref{#1}}
\newcounter{lcnum} %Likely change number
\newcommand{\lthelcnum}{LC\thelcnum}
\newcommand{\lcref}[1]{LC\ref{#1}}

\usepackage{fullpage}

\newcommand{\deftheory}[9][Not Applicable]
{
\newpage
\noindent \rule{\textwidth}{0.5mm}

\paragraph{RefName: } \textbf{#2} \phantomsection 
\label{#2}

\paragraph{Label:} #3

\noindent \rule{\textwidth}{0.5mm}

\paragraph{Equation:}

#4

\paragraph{Description:}

#5

\paragraph{Notes:}

#6

\paragraph{Source:}

#7

\paragraph{Ref.\ By:}

#8

\paragraph{Preconditions for \hyperref[#2]{#2}:}
\label{#2_precond}

#9

\paragraph{Derivation for \hyperref[#2]{#2}:}
\label{#2_deriv}

#1

\noindent \rule{\textwidth}{0.5mm}

}

\begin{document}

\title{Software Requirements Specification for \progname: subtitle describing software} 
\author{\authname}
\date{\today}
	
\maketitle

~\newpage

\pagenumbering{roman}

\tableofcontents

~\newpage

\section*{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
Date 1 & 1.0 & Notes\\
Date 2 & 1.1 & Notes\\
\bottomrule
\end{tabularx}

\newpage

\pagenumbering{arabic}


\section{Introduction}

\plt{The introduction section is written to introduce the problem.  It starts
  general and focuses on the problem domain. The general advice is to start with
a paragraph or two that describes the problem, followed by a ``roadmap''
paragraph.  A roadmap orients the reader by telling them what sub-sections to
expect in the Introduction section.}

\subsection{Purpose of Document}

\plt{This section summarizes the purpose of the SRS document.  It does not focus
  on the problem itself.  The problem is described in the ``Problem
  Description'' section (Section~\ref{Sec_pd}).  The purpose is for the document
  in the context of the project itself, not in the context of this course.
  Although the ``purpose'' of the document is to get a grade, you should not
  mention this.  Instead, ``fake it'' as if this is a real project.  The purpose
  section will be similar between projects.  The purpose of the document is the
  purpose of the SRS, including communication, planning for the design stage,
  etc.}

\subsection{Characteristics of Intended Reader} \label{sec_IntendedReader} 

The intended readers of this SRS document include project managers, software developers, testing engineers, and stakeholders directly involved in the design and implementation of the software system. Project managers and testing engineers would be directly involved in the development and testing process. They would generally have an education in computer science along with experience in software design, web or mobile development, and software testing. Project managers generally have experience in managing software projects and knowledge of software development processes. Stakeholders like doctors and nursing staff would have domain knowledge and could provide insights to understand the clinical workflow and documentation process. 

\subsection{Scope of Requirements} 

\plt{Modelling the real world requires simplification.  The full complexity of
  the actual physics, chemistry, biology is too much for existing models, and
  for existing computational solution techniques.  Rather than say what is in
  the scope, it is usually easier to say what is not.  You can think of it as
  the scope is initially everything, and then it is constrained to create the
  actual scope.  For instance, the problem can be restricted to 2 dimensions, or
  it can ignore the effect of temperature (or pressure) on the material
  properties, etc.}  

\plt{The scope section is related to the assumptions section
  (Section~\ref{sec_assumpt}).  However, the scope and the assumptions are not
  at the same level of abstraction.  The scope is at a high level.  The focus is
  on the ``big picture'' assumptions.  The assumptions section lists, and
  describes, all of the assumptions.}

\plt{The scope section is relevant for later determining typical values of inputs. The scope should make it clear what inputs are reasonable to expect. This is a distinction between scope and context (context is a later section).  Scope affects the inputs while context affects how the software will be used.}

\plt{The goal statements refine the ``Problem Description''
  (Section~\ref{Sec_pd}).  A goal is a functional objective the system under
  consideration should achieve. Goals provide criteria for sufficient
  completeness of a requirements specification and for requirements
  pertinence. Goals will be refined in Section “Instanced Models”
  (Section~\ref{sec_instance}). Large and complex goals should be decomposed
  into smaller sub-goals.  The goals are written abstractly, with a minimal
  amount of technical language.  They should be understandable by non-domain
  experts.}

\noindent Given the \plt{inputs}, the goal statements are:

\begin{itemize}
\item[GS\refstepcounter{goalnum}\thegoalnum \label{G_meaningfulLabel}:] \plt{One
    sentence description of the goal.  There may be more than one.  Each Goal
    should have a meaningful label.}
\end{itemize}

% References at the end of the document

\subsection{Organization of Document}

\plt{This section provides a roadmap of the SRS document.  It will help the
  reader orient themselves.  It will provide direction that will help them
  select which sections they want to read, and in what order.  This section will
  be similar between project.}

~\newpage

\section{System Description}

\subsection{Definitions, Acronyms, and Abbreviations}

\begin{tabular}{l l} 
  \toprule    
  \textbf{symbol} & \textbf{description}\\
  \midrule 
  A & Assumption\\
  GD & General Definition\\
  GS & Goal Statement\\
  LC & Likely Change\\
  R & Requirement\\
  SRS & Software Requirements Specification\\
  EHR & Electronic Healthcare record\\
  \bottomrule
\end{tabular}\\

The following is the glossary for this document:

\textbf{System} -- When referring to a system the document refers to the intended solution/product.

\textbf{User} -- When referring to a user the document refers to a person who will use the product.

\subsection{System overview}

\subsection{System Functionality}

This section outlines the core functionalities and characteristics of the proposed system:

\begin{itemize}
  \item \textbf{Patient Documentation} -- The system should facilitate efficient and streamlined patient documentation throughout the EHR documentation process. This includes storing patient data, clinical notes, treatment plans, and patient history in a secure mamnner.
  
  \item \textbf{Voice Recording and Transcription} -- The system should be able to record conversations between healthcare professionals and patients which will be transcribed to fill out charts and patient profiles efficiently.
  
  \item \textbf{Real-time Data Access} –- The users must have real-time access to patient data and documentation enabling them to make informed decisions quickly and efficiently.
  
  \item \textbf{Automated Medicine Suggestions} –- The system should be able to provide automated medicine suggestions based on the transcribed data which will help users to fill out the charts faster and make informed treatment decisions.
  
  \item \textbf{Automated Diagnosis Suggestions} -- The system should be able to suggest possible diagnoses based on transcribed data which will help users to make faster and more accurate diagnoses.
  
  \item \textbf{User Authentication} -- The system must provide secure user authentication methods to ensure that only authorized personnel can access sensitive patient information.
  
  \item \textbf{Data Privacy} -- The system must store all patient data in a secure manner to avoid any data privacy and regulatory concerns.
  
\end{itemize}


\subsection{User Characteristics} \label{SecUserCharacteristics}

The intended users of this product are healthcare professionals, specifically those involved in patient documentation, including doctors, nurses, and other clinical administrative staff. 

The following are the user characteristics associated with the intended users:

\textbf{Education Level} -- All users are expected to have a minimum of a college diploma and basic reading, writing, and speaking skills. The education level of the intended users will vary based on their role, generally a bachelor’s degree or college diploma in nursing, medicine, or other healthcare fields. 

\textbf{Experience} -- All users will be expected to have basic familiarity with EHR systems or similar applications. This experience will depend on their roles ranging from entry-level positions to experienced professionals. 

\textbf{Technical Expertise} -- The users should have basic technical skills to use EHR systems and other healthcare software applications. In addition to this, the users should have familiarity with data entry processes and analytics interpretation.

\textbf{Accessibility Considerations} -- It is anticipated that some users may have accessibility issues. The user interface should be designed for ease of navigation, incorporating various accessibility features.

Specific requirements must be specified to accommodate users with varying technical expertise and diverse educational backgrounds. This will ensure the application is usable by all healthcare staff, regardless of their abilities.


\subsection{System Constraints}

The following constraints will guide the system design and implementation:

\begin{itemize} 
  \item \textbf{System Compatibility} -- The system must be compatible with existing EHR systems for seamless integration and data exchange.

  \item \textbf{Compliance with Regulatory Standards} -- The system must adhere to healthcare regulations ensuring the confidentiality and security of patient data.

  \item \textbf{User Accessibility} -- The system must meet established accessibility standards to ensure usability for all healthcare staff, including those with disabilities.

  \item \textbf{Cost and Time} -- The system must be developed within the imposed budget and time restrictions.

\end{itemize}

\subsubsection{Assumptions and Dependencies} \label{sec_assumpt}

\subsubsection{Usage Scanerios}


~\newpage

\section{Requirements}

This section provides the functional requirements, the business tasks that the
software is expected to complete, and the nonfunctional requirements, the
qualities that the software is expected to exhibit.

\subsection{Functional Requirements}

\noindent \begin{itemize}

\item[R\refstepcounter{reqnum}\thereqnum \label{R_Inputs}:] \plt{Requirements
    for the inputs that are supplied by the user.  This information has to be
    explicit.}

\item[R\refstepcounter{reqnum}\thereqnum \label{R_OutputInputs}:] \plt{It isn't
    always required, but often echoing the inputs as part of the output is a
    good idea.}

\item[R\refstepcounter{reqnum}\thereqnum \label{R_Calculate}:] \plt{Calculation
    related requirements.}

\item[R\refstepcounter{reqnum}\thereqnum \label{R_VerifyOutput}:]
  \plt{Verification related requirements.}

\item[R\refstepcounter{reqnum}\thereqnum \label{R_Output}:] \plt{Output related
    requirements.}

\end{itemize}

\plt{Every IM should map to at least one requirement, but not every requirement
  has to map to a corresponding IM.}

\subsection{Non-functional Requirements}

\noindent \begin{itemize}

\item[NFR\refstepcounter{nfrnum}\thenfrnum \label{NFR_Performance}:] \textbf{Performance}  
    
    \textbf{Requirement:} The system shall process voice recordings and convert them into medical charts within 30 seconds of recording completion.  
  
    \textbf{Rationale:} Quick documentation is critical to streamline the patient journey and reduce healthcare professionals' workload.  
  
    \textbf{Fit Criterion:} The system will consistently generate completed documentation in under 30 seconds.  
  
    \textbf{Dependencies:} Dependent on the speech-to-text engine and cloud infrastructure.  
  
    \textbf{Normal Operation:} Under typical conditions, the system will handle up to 100 voice recordings per hour without performance degradation.  
  
    \textbf{Undesired Event Handling:} If the system takes longer than 30 seconds, an alert will be triggered, and the system will attempt to resolve delays by reducing background processes or scaling resources.

\item[NFR\refstepcounter{nfrnum}\thenfrnum \label{NFR_Reliability}:] \textbf{Reliability}  

    \textbf{Requirement:} The system shall have a 99.9\% uptime guarantee during operational hours (9 AM to 9 PM).  
  
    \textbf{Rationale:} Reliability is critical to ensure uninterrupted service for healthcare professionals, particularly in time-sensitive environments like emergency rooms.  
  
    \textbf{Fit Criterion:} System logs will confirm an uptime rate of 99.9\% over a 30-day period.  
  
    \textbf{Dependencies:} Cloud infrastructure, hosting services, and local hardware resilience.  
  
    \textbf{Undesired Event Handling:} If uptime falls below 99.9\%, an automated system will switch to backup servers within 10 seconds to ensure continuity of service.

\item[NFR\refstepcounter{nfrnum}\thenfrnum \label{NFR_Scalability}:] \textbf{Scalability}  

    \textbf{Requirement:} The system shall be able to scale to accommodate up to 500 simultaneous users without affecting performance.  
  
    \textbf{Rationale:} The system must support multiple healthcare providers across various locations, particularly during peak hours.  
  
    \textbf{Fit Criterion:} The system will maintain performance benchmarks (processing under 30 seconds) even when 500 users are active.  
  
    \textbf{Dependencies:} Cloud infrastructure for auto-scaling capabilities.  
  
    \textbf{Normal Operation:} The system will maintain user load without affecting response time.  
  
    \textbf{Undesired Event Handling:} In case of unexpected spikes in usage, the system will dynamically allocate additional cloud resources to manage the load without affecting current users.

\item[NFR\refstepcounter{nfrnum}\thenfrnum \label{NFR_Security}:] \textbf{Security}  

    \textbf{Requirement:} The system shall encrypt all patient data, both in transit and at rest, following HIPAA standards.  
  
    \textbf{Rationale:} Ensuring patient confidentiality and compliance with healthcare data regulations is essential.  
  
    \textbf{Fit Criterion:} Security audits will show 100\% compliance with HIPAA and encryption standards.  
  
    \textbf{Dependencies:} Encryption services and security protocols in the cloud infrastructure.  
  
    \textbf{Undesired Event Handling:} If a security breach is detected, the system will immediately log out all users, lock access to sensitive data, and alert system administrators.

\item[NFR\refstepcounter{nfrnum}\thenfrnum \label{NFR_Usability}:] \textbf{Usability}  

    \textbf{Requirement:} The system’s user interface shall be intuitive, allowing healthcare professionals to complete documentation with minimal training (less than 30 minutes of training).  
  
    \textbf{Rationale:} A user-friendly interface reduces learning time and increases adoption among healthcare providers.  
  
    \textbf{Fit Criterion:} Usability tests will show that 90\% of healthcare professionals can navigate the system with less than 30 minutes of instruction.  
  
    \textbf{Dependencies:} Usability design and feedback loops during development.  
  
    \textbf{Undesired Event Handling:} If users encounter usability issues, they can access live chat support integrated within the application.

\item[NFR\refstepcounter{nfrnum}\thenfrnum \label{NFR_Maintainability}:] \textbf{Maintainability}  

    \textbf{Requirement:} The system shall be updated with new features without causing downtime for more than 5 minutes.  
  
    \textbf{Rationale:} Frequent updates should not disrupt healthcare professionals during critical hours.  
  
    \textbf{Fit Criterion:} Release notes and system logs will show that updates occur with less than 5 minutes of downtime, or during non-operational hours.  
  
    \textbf{Dependencies:} Continuous integration and delivery pipelines.  
  
    \textbf{Undesired Event Handling:} In case of an update failure, the system will automatically revert to the last stable version.

\item[NFR\refstepcounter{nfrnum}\thenfrnum \label{NFR_Compatibility}:] \textbf{Compatibility}  

    \textbf{Requirement:} The system shall be compatible with major operating systems (Windows, macOS, and Linux) and dictation devices.  
  
    \textbf{Rationale:} Healthcare providers use a variety of platforms, and the system must be versatile to support their workflows.  
  
    \textbf{Fit Criterion:} Compatibility tests will show full functionality on all major operating systems and devices used for dictation.  
  
    \textbf{Dependencies:} Device drivers and OS compatibility libraries.  
  
    \textbf{Undesired Event Handling:} If a compatibility issue arises, the system will notify the user and suggest an alternative setup or device.

\item[NFR\refstepcounter{nfrnum}\thenfrnum \label{NFR_DataIntegrity}:] \textbf{Data Integrity}  

    \textbf{Requirement:} The system shall prevent duplicate or erroneous data entries when processing voice recordings.  
  
    \textbf{Rationale:} Data accuracy is critical in healthcare documentation, where errors could lead to incorrect treatment or diagnosis.  
  
    \textbf{Fit Criterion:} Data audits will show no more than 0.1\% duplication or errors in generated medical charts.  
  
    \textbf{Dependencies:} Data validation protocols and the speech-to-text engine.  
  
    \textbf{Undesired Event Handling:} In case of detected duplicates or errors, the system will automatically flag the entry for review and notify the healthcare professional.

\end{itemize}

\subsection{Rationale}

\plt{Provide a rationale for the decisions made in the documentation.  Rationale
should be provided for scope decisions, modelling decisions, assumptions and
typical values.}

\section{Likely Changes}    

\noindent \begin{itemize}

\item[LC\refstepcounter{lcnum}\thelcnum\label{LC_meaningfulLabel}:] \plt{Give
    the likely changes, with a reference to the related assumption (aref), as appropriate.}

\end{itemize}

\section{Unlikely Changes}    

\noindent \begin{itemize}

\item[LC\refstepcounter{lcnum}\thelcnum\label{LC_meaningfulLabel}:] \plt{Give
    the unlikely changes.  The design can assume that the changes listed will
    not occur.}

\end{itemize}

~\newpage

\section{References}

\newpage{}
\section*{Appendix --- Reflection}

\wss{Not required for CAS 741}

The information in this section will be used to evaluate the team members on the
graduate attribute of Lifelong Learning.  

\input{../Reflection.tex}

\begin{enumerate}
  \item What went well while writing this deliverable? 
  \item What pain points did you experience during this deliverable, and how did
  you resolve them?
  \item How many of your requirements were inspired by speaking to your
  client(s) or their proxies (e.g. your peers, stakeholders, potential users)?
  \item Which of the courses you have taken, or are currently taking, will help
  your team to be successful with your capstone project.
  \item What knowledge and skills will the team collectively need to acquire to
  successfully complete this capstone project?  Examples of possible knowledge
  to acquire include domain specific knowledge from the domain of your
  application, or software engineering knowledge, mechatronics knowledge or
  computer science knowledge.  Skills may be related to technology, or writing,
  or presentation, or team management, etc.  You should look to identify at
  least one item for each team member.
  \item For each of the knowledge areas and skills identified in the previous
  question, what are at least two approaches to acquiring the knowledge or
  mastering the skill?  Of the identified approaches, which will each team
  member pursue, and why did they make this choice?
\end{enumerate}

\end{document}